A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex
typo

Python is commonly selected as the programming language of choice in scientific
communities, and in particular, for our use case of neuroscience, where
numerous specialized Python libraries exist to study the data.
While serialization of Python to Java may lead to significant overheads, we
chose to focus on Spark Python API due to its suitability for neuroimaging
research.

>>>>

Python is commonly selected as the programming language of choice in scientific
communities, and in particular, for our use case of neuroscience, where
numerous specialized Python libraries exist to study the data.
While serialization of Python to Java may lead to significant overheads, we
chose to focus on PySpark API due to its suitability for neuroimaging
research.
